Geometric Signs on Paleolithic Mobile Objects as Cultural Group Markers

### 2025-02-11 endofquarterpaper.qmd
time period

The modularity test, when run on the above groupings, resulted in a score of `r as_group`. The perMANOVA test produced an R-squared value of `r perman_r` and a P value of `r perman_p`, which tells us that the groupings are statisically significant, and that 52% of the variability in the sign distribution can be attributed to group membership. The multivariate homogeneity test of group dispersions produced @fig-perm-disp, showing that the overlap between groups is fairly minimal.

>>>>

The modularity test, when run on the above groupings, resulted in a score of `r as_group`. The perMANOVA test produced an R-squared value of `r perman_r` and a P value of `r perman_p`, which tells us that the groupings are statistically significant, and that 52% of the variability in the sign distribution can be attributed to group membership. The multivariate homogeneity test of group dispersions produced @fig-perm-disp, showing that the overlap between groups is fairly minimal.
